TITLE

### 2021-02-25 outputs/Paper.Rmd
update

## Descriptive Analysis

```{r read_data, include=FALSE}

@@

>>>>

## Descriptive Analysis
```{r read_data, include=FALSE}

@@

```{r size,echo=FALSE}
# Get the number of rows
size<- nrow(simulated_data)
```

After discussing data gathering method, we sampled data in R. We totally have **`r size`** observations, and 14 of following features according to the questionnaires.

* `type` : Unique row identifier for Open Data database
* `Q1` : Unique row identifier for Open Data database
* `Q2` : Unique row identifier for Open Data database
* `Q3` : Unique row identifier for Open Data database
* `Q4` : Unique row identifier for Open Data database
* `Q5` : Unique row identifier for Open Data database
* `Q6` : Unique row identifier for Open Data database
* `Q7` : Unique row identifier for Open Data database
* `Q8` : Unique row identifier for Open Data database
* `Q9` : Unique row identifier for Open Data database
* `Q10` : Unique row identifier for Open Data database
* `Q11` : Unique row identifier for Open Data database
* `Q12` : Unique row identifier for Open Data database
* `Q13` : Unique row identifier for Open Data database
* `Q14` : Unique row identifier for Open Data database
